# Data management

**Chapter progress bar**

```{r echo = F, results = 'asis'}

printProgressBar(.35)

```

Once we got access to the Twitter API we must start planning about data management. The Twitter API can potentially return a huge amount of data (the current limits for Academic access are set to 10,000,000 tweets a month). What do we do with it? Where do we store it but also should we store it? 

## JSON

The default format for data loads from the Twitter API is JSON. A JSON (JavaScript Object Notation) file is a plain text file - so you can open it with any text editor. Information is structured through nesting like HTML or XML. JSON can't be naturally manipulated in R. Access and analysis in R involves reading the text in but also transforming it into R vector *types* (e.g. `logical`, `integer`, `double`, `character`) and *structures* (e.g. atomic vector, `data.frame`, `matrix`, `list`) - which is not painless!  


### Read your JSON files: Tweets

```{r eval = F}

json_data_dir <- 
  "json_data"

if(!dir.exists(json_data_dir)) {
  dir.create(json_data_dir)
}

files <- 
  list.files(json_data_dir)

tweet_data.df <- 
  data.frame()

for(file in files) {
  
  print(sprintf("File missing: %s", 
                length(files) - which(file %in% files)))
  
  obj.r <- 
    jsonlite::read_json(sprintf("%s/%s", json_data_dir, file))
  
  for (i in 1:length(obj.r$data)) {
    
    this_tweet.df <- 
      data.frame(id = 
                   obj.r$data[[i]]$id[[1]][[1]],
                 author_id = 
                   obj.r$data[[i]]$author_id[[1]][[1]],
                 created_at = 
                   obj.r$data[[i]]$created_at[[1]][[1]],
                 lang = 
                   obj.r$data[[i]]$lang[[1]][[1]],
                 reply_settings = 
                   obj.r$data[[i]]$reply_settings[[1]][[1]],
                 source  = 
                   obj.r$data[[i]]$source[[1]][[1]],
                 possibly_sensitive = 
                   obj.r$data[[i]]$possibly_sensitive[[1]][[1]],
                 conversation_id = 
                   obj.r$data[[i]]$conversation_id[[1]][[1]],
                 text = 
                   obj.r$data[[i]]$text[[1]][[1]])

    these_metrics <- 
      as.data.frame(obj.r$data[[i]]$public_metrics)
    
    colnames(these_metrics) <- 
      names(obj.r$data[[i]]$public_metrics)
    
    this_tweet.df <- 
      this_tweet.df %>%
      dplyr::bind_cols(these_metrics)
    
    tweet_data.df <- 
      tweet_data.df %>%
      dplyr::bind_rows(this_tweet.df)

  }
  
}

```


## Storage, analysis and acccess

## Data ownership and ethics