# User follows

**Chapter progress bar**

```{r echo = F, results = 'asis'}

printProgressBar(.9)

```

There are different ways to get the users that a given user follows.  


```{r echo = FALSE, results = 'show', out.width = '40%'}

library(DiagrammeR)
library(data.table)

niv <- 
  c("User A\\n(entry point)", "User B", "User C", "User D")
widths <- 
  c(.8, .5, .5, .5)
colors <-
  c("red", "blue", "blue", "blue")
from <- 
  c("User A\\n(entry point)", "User A\\n(entry point)", "User A\\n(entry point)")
to <- 
  c("User B", "User C", "User D")

temp <- 
  data.table::data.table(from = factor(from, levels=niv),
                         to = factor(to, levels=niv))

nodes <-   
  DiagrammeR::create_node_df(n=length(niv), label=niv,  width=widths, color = colors) 

edges <- 
  DiagrammeR::create_edge_df(from = temp$from, 
                             to = temp$to, 
                             rel = "leading_to", 
                             label = c("follows"))

graph <- 
  create_graph(nodes_df = nodes, edges_df = edges)

render_graph(graph)

```

If we are interested in getting only the Twitter `user_id` of each user out entry point user follows we can use this API endpoint (at this time a corresponding v2 version is not available as far as I know)

```{r}

url <- 
  "https://api.twitter.com/1.1/friends/ids.json"

```

and this parameters 

```{r}

entry_point_user_id <- 
  '2962620002'

params <- 
  list(user_id = entry_point_user_id,
       count = 5000)

```

The only required parameter is the `user_id` or alternatively `screen_name`.

We store the JSON-formatted results into a data folder which we set with

```{r eval = F}

json_data_dir <- 
  "json_data"

if(!dir.exists(json_data_dir)) {
  dir.create(json_data_dir)
}

```

We are now ready to request a paginate the results (in case we our entry point user follows more than 5,000 users).

```{r}

headers <- 
  c(`Authorization` = sprintf('Bearer %s', 
                              Sys.getenv("BEARER_TOKEN")))

res <- 
  httr::GET(url,
            httr::add_headers(.headers = headers),
            query = params)

```

```{r}

obj.r <- 
  httr::content(res, as = "text") %>%
  jsonlite::fromJSON()

jsonlite::write_json(httr::content(res, as = "parsed"), 
                     path = sprintf("%s/%s_follows_ids_%s.json",
                                    json_data_dir,
                                    entry_point_user_id,
                                    sprintf("%04d", 1)))

```

Do we have additional pages? 

```{r eval = F}

if (obj.r$next_cursor != 0) {
  
  counter <- 2
  
  while(TRUE) {
    
    params[['cursor']] <-
      obj.r$next_cursor_str
    
    print(sprintf("Next cursor: %s...", obj.r$next_cursor_str))
    
    res <- 
      httr::GET(url,
                httr::add_headers(.headers = headers),
                query = params)
    
    obj.r <- 
      httr::content(res, as = "text") %>%
      jsonlite::fromJSON()
    
    if (!is.null(obj.r$error) && obj.r$error['code'] == 88) {
      
      while(TRUE) {
        
        print(obj.r$errors)
        
        Sys.sleep(60)
        
        res <- 
          httr::GET(url,
                    httr::add_headers(.headers = headers),
                    query = params)
        
        obj.r <- 
          httr::content(res, as = "text") %>%
          jsonlite::fromJSON()
        
        if (is.null(obj.r$errors)) {
          
          break
          
        } 
        
      }
      
    }
    
    jsonlite::write_json(httr::content(res, as = "parsed"), 
                         path = sprintf("%s/%s_follows_ids_%s.json",
                                        json_data_dir,
                                        entry_point_user_id,
                                        sprintf("%04d", counter)))
    
    
    if (obj.r$next_cursor == 0) {
      
      break
      
    }
    
    counter <- 
      counter + 1
    
  }
  
}


```

